Estimating the \gc{genome-wide} contribution of selection to temporal allele frequency change.

### 2019-09-23 manuscript/manuscript.tex
updated abstract

\title{Estimating the contribution of selection to temporal allele frequency change}

@@

\begin{abstract}

  Adaptation can proceed in natural populations and selection experiments over
  very short timescales.  However, detecting these changes genome-wide is
  difficult, as rapid adaptation often proceeds from standing variation or is
  the result of selection on polygenic traits, both of which may leave faint
  genomic signals indistinguishable from a noisy background of genetic drift.
  One promising signal comes from the genome-wide covariance between allele
  frequency changes observable from temporal genomic data, e.g.
  evolve-and-resequence studies. These temporal covariances reflect how the
  change in neutral allele frequency at one timepoint is predictive of the
  changes at later timepoints when there is heritable fitness variation in the
  population, as neutral alleles can remain associated with selected alleles
  over time. Since genetic drift does not lead to temporal covariance, we can
  use these covariances to estimate what fraction of the variation in allele
  frequency change through time is driven by linked selection. Here, we
  reanalyze two \emph{Drosophila simulans} evolve-and-resequence studies, and
  one artificial selection experiment in mice, to quantify the effects of
  linked selection over short timescales.  Additionally, taking advantage of
  selection on replicated populations, we can estimate the covariance in allele
  frequency between replicates due to convergent selection pressure.  We also
  identify signals of negative temporal covariance corresponding to reversals
  in the direction of selection for a reasonable proportion of loci over the time
  course of a selection experiment.  Overall, we find that in the three studies
  we analyzed, linked selection has a significant impact on short-term allele
  frequency dynamics that previously may have been attributed to genetic drift

>>>>

\title{Estimating the \gc{genome-wide} contribution of selection to temporal allele frequency change.}

@@

\begin{abstract}
% Adaptation can proceed in natural populations and selection experiments over
% very short timescales.
 \gc{Rapid phenotypic adaptation is often observed in natural populations and selection experiments.}
 However, detecting the \gc{impact of this selection} genome-wide is
  difficult, as\gc{such} adaptation often proceeds from standing
  variation \gc{and} selection on \gc{highly} polygenic traits, both of which may leave faint
  genomic signals indistinguishable from a noisy background of genetic drift.
  One promising signal comes from the genome-wide covariance between allele
  frequency changes observable from temporal genomic data, e.g.
  evolve-and-resequence studies. These temporal covariances reflect how the
  change in neutral allele frequency at one timepoint is predictive of the
  changes at later timepoints when there is heritable fitness variation in the
  population, as neutral alleles can remain associated with selected alleles
  over time. Since genetic drift does not lead to temporal covariance, we can
  use these covariances to estimate what fraction of the variation in allele
  frequency change through time is driven by linked selection. Here, we
  reanalyze two \emph{Drosophila simulans} evolve-and-resequence studies, and
  one artificial selection experiment in mice, to quantify the effects of
  linked selection over short timescales using covariance among
  time-points and across replicates. \gc{We estimate that over 20\% {\bf ??} of allele frequency
  change in these experiments is driven by selection.} \gc{Against
  this background of positive genome-wide tmeporal covariances} We also
  identify signals of negative temporal covariance corresponding to reversals
  in the direction of selection for a reasonable proportion of loci over the time
  course of a selection experiment.  Overall, we find that in the three studies
  we analyzed, linked selection has a \gc{large} impact on short-term allele
  frequency dynamics \gc{that is readily distinguishable from} genetic drift.

  %  Additionally, taking advantage of
  %selection on replicated populations, we can estimate the covariance in allele
  %frequency between replicates due to convergent selection
  %\gc{pressures}.
